Make any stupid plot you want

### 2021-02-28 draft/sections/math.tex
overthinking 3d

\begin{figure}[H]
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/math/temp_2f.png}
        \caption{}
        \label{fig:fiber_example_plane}
    \end{subfigure}
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/math/temp_3f.png}
        \caption{}
        \label{fig:fiber_example_cube}
    \end{subfigure}
    \caption{These two datasets have the same base space \dbase\, but figure~\ref{fig:fiber_example_plane} has fiber  $\dfiber=\reals\times\reals$ which is (time, temperature) while figure~\ref{fig:fiber_example_cube} has fiber $\realsp\times\reals^2$ which is (time, wind=(speed, direction))}
    \label{fig:data_fiber_example}
\end{figure}

>>>>

\begin{figure}[H]
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/math/temp_1k.png}
        \caption{}
        \label{fig:fiber_example_plane}
    \end{subfigure}
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/math/temp_3f.png}
        \caption{}
        \label{fig:fiber_example_cube}
    \end{subfigure}
    \caption{These two datasets have the same base space \dbase\ of discrete points, but figure~\ref{fig:fiber_example_plane} has fiber  $\dfiber=\reals\times\reals$ which is (time, temperature) while figure~\ref{fig:fiber_example_cube} has fiber $\reals\times\realsp\times\reals$ which is (time, wind=(speed, direction))}
    \label{fig:data_fiber_example}
\end{figure}
